Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-09-07 sections/discussion.tex
fix merge conflicts

%\subsection{Reasons of Classification}
% reasons for classification as useful or not useful
\subsection{What decisions are made during the manual classification?}
During manual comment usefulness assessment, we recorded the participants' rationale to verify that the comments actually direct contribute to the proposed changes. We can summarize that most of reasons for \texttt{YES} voting are: the comments 1) contain new information 2) contain constructive suggestions, 3) discuss directly to the proposed changes, and 4) discuss specific technical matters. For \texttt{NO} voting, we can summarize that the comments 1) are chatting (just communication), 2) talking about matters unrelated to the proposed changes, 3) discuss about process workflow and supporting system (e.g. Git and Gerrit).
%During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:
%
%\begin{itemize}
%	\item they contain new information;
%	\item they contain constructive suggestions;
%	\item they discuss directly about the change; and
%	\item they discuss technical matters.
%\end{itemize}
%
%Examples of reasons for negative comments include:
%
%\begin{itemize}
%	\item chatting (i.e. no new information, just communication);
%	\item not discussing directly about the change;
%	\item discussing about the process workflow; and
%	\item discussing about Git or Gerrit itself.
%\end{itemize}

>>>>

%\subsection{Reasons of Classification}
% reasons for classification as useful or not useful

%\subsection{What decisions are made during the manual classification?}
%During manual comment usefulness assessment, we recorded the participants' rationale to verify that the comments are actually technically or little direct contribute to the proposed changes. We can summarize that most of reason for \texttt{YES} voting are: the comments 1) contain new information 2) contain constructive suggestions, 3) discuss directly to the proposed changes, and 4) discuss the technical matters. For \texttt{NO} voting, we can summarize that the comments 1) are chatting (just communication), 2) talking about matters unrelated to the proposed changes, 3) discuss about process workflow and supporting system (e.g. Git and Gerrit).

%During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:
%
%\begin{itemize}
%	\item they contain new information;
%	\item they contain constructive suggestions;
%	\item they discuss directly about the change; and
%	\item they discuss technical matters.
%\end{itemize}
%
%Examples of reasons for negative comments include:
%
%\begin{itemize}
%	\item chatting (i.e. no new information, just communication);
%	\item not discussing directly about the change;
%	\item discussing about the process workflow; and
%	\item discussing about Git or Gerrit itself.
%\end{itemize}
